---
title: "Phoebe Woodworth-Jefcoats, PhD"
format: 
  closeread-html:
    cr-style:
      section-background-color: white
    theme: [zephyr, custom.scss]
---

Kaneohe, HI  |  (808) 358-7767  |  <phoebe.jefcoats@gmail.com>  
[pwj-dataviz.com](https://www.pwj-dataviz.com)  |  LinkedIn: [pwoodworth-jefcoats](http://www.linkedin.com/in/pwoodworth-jefcoats)  |  GitHub: [pwoodworth-jefcoats](https://github.com/pwoodworth-jefcoats)  |  ORCiD: [0000-0001-9353-923X](https://orcid.org/0000-0001-9353-923X)  

## Professional Summary
I have over 20 years of experience turning large datasets into easy-to-understand
graphics and reports, all backed by thorough data analysis.  I'm adept at workflows
that merge data analysis and communication product development, including incorporating
branding standards.  Across my work, I focus on using data to provide clarity, tell
stories, and inform decisions for audiences ranging from technical experts to casual
readers.  I embrace collaborative open science and contribute to the development of
tools, templates, best practice guides, and hands-on training.  
\
Scroll through my resume and CV below.  Mouse over the graphics for more details.

```{r}
#| include: false
#| message: false
#| warning: false

# Global setup
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE
)
```

::::{.cr-section}

## My Resume

Employment @cr-jobs

:::{#cr-jobs}
```{r, message = FALSE}
# Load packages
library(tidyverse, quietly = TRUE)
library(here)
library(ggiraph) # For interactive elements

# Following an example from:
# https://r-graph-gallery.com/web-vertical-line-chart-with-ggplot2.html
# with an assist from phind.com and 
# https://github.com/clementrx/Closeread-Prize/blob/main/index.qmd

# Load data
jobs <- read.csv(here("CV", "Data", "Employment.csv"))
labels <- read.csv(here("CV", "Data", "TimelineLabels.csv"))
labels_jobs <- labels |>
  filter(category == "job")

# This is tedius, but not sure of a better way
lj1 <- labels |>
  filter(category == "job_1")
lj2 <- labels |>
  filter(category == "job_2")
lj3 <- labels |>
  filter(category == "job_3")

employ_interactive <- ggplot() +
  geom_segment_interactive(data = jobs, aes(x = Start, y = 10,
                                            xend = End, yend = 10,
                                            color = Employer,
                                            tooltip = Focus),
                           linewidth = 3,
                           show.legend = FALSE) +
  geom_text(data = labels_jobs, aes(x = x, y = y, label = label),
            size = 4,
            hjust = 0,
            show.legend = FALSE) +
  geom_text(data = lj1, aes(x = x, y = y, label = label),
            color = "#003087",
            size = 4,
            hjust = 0,
            show.legend = FALSE) +
  geom_text(data = lj2, aes(x = x, y = y, label = label),
            color = "#77BDE7",
            size = 4,
            hjust = 0,
            show.legend = FALSE) +
  geom_text(data = lj3, aes(x = x, y = y, label = label),
            color = "#3366cc",
            size = 4,
            hjust = 0,
            show.legend = FALSE) +
  scale_y_continuous(
    limits = c(0, 100),
    position = "left") +
  scale_x_continuous(
    limits = c(2002, 2026)) +
  scale_color_manual(values = c("#77BDE7", "#3366cc", "#003087")) +
  theme_void() +
  coord_flip() 

girafe(ggobj = employ_interactive,
       options = list(
         opts_tooltip(
           opacity = 0.9
         )
       )
       )

```
:::

Education @cr-schools

:::{#cr-schools}
```{r}
# Load data
school <- read.csv(here("CV", "Data", "Education.csv"))

labels_school <- labels |>
  filter(category == "degree")

# Build on previous plot
# which means replicating code from above
edu_interactive <- ggplot() +
geom_segment_interactive(data = jobs, aes(x = Start, y = 10,
                                            xend = End, yend = 10,
                                            color = Employer,
                                            tooltip = Focus),
                           linewidth = 3,
                           show.legend = FALSE) +
  geom_text(data = labels_jobs, aes(x = x, y = y, label = label),
            size = 4,
            hjust = 0,
            show.legend = FALSE) +
  geom_text(data = lj1, aes(x = x, y = y, label = label),
            color = "#003087",
            size = 4,
            hjust = 0,
            show.legend = FALSE) +
  geom_text(data = lj2, aes(x = x, y = y, label = label),
            color = "#77BDE7",
            size = 4,
            hjust = 0,
            show.legend = FALSE) +
  geom_text(data = lj3, aes(x = x, y = y, label = label),
            color = "#3366cc",
            size = 4,
            hjust = 0,
            show.legend = FALSE) +
  scale_y_continuous(
    limits = c(0, 100),
    position = "left") +
  scale_x_continuous(
    limits = c(2002, 2026)) +
  scale_color_manual(values = c("#77BDE7", "#3366cc", "#003087")) +
  theme_void() +
  coord_flip() +
# new stuff added to plot
geom_point_interactive(data = school, aes(x = Date, y = 10, tooltip = Focus),
           shape = 21, color = "white", fill = "black", size = 5, stroke = 0.7,
           show.legend = FALSE) +
geom_text(data = labels_school, aes(x = x, y = y, label = label),
          size = 4,
          hjust = 0,
          show.legend = FALSE)

girafe(ggobj = edu_interactive,
       options = list(
         opts_tooltip(
           opacity = 0.9
         )
       )
       )
```
:::

::::

::::{.cr-section}
## My CV

Overview of my publications by year, type, and personal contribution: @cr-pub-tree

:::{#cr-pub-tree}
```{r}
# Decided to keep this for now
library(treemapify)

# Colors from paletteer_d("rockthemes::secondlaw"), but black switched out

Products <- read_csv(here("CV", "Data", "Products.csv"), show_col_types = FALSE)

Products_byYearTypeAuthor <- Products %>%
  count(Year, Type, Author)

ggplot(Products_byYearTypeAuthor, aes(area = n, fill = Author, label = Author,
                                      subgroup = Year,
                                      subgroup2 = Type)) +
  geom_treemap() +
  scale_fill_discrete(name = "Authorship",
                      type = c("#808080", "#58958C", "#9D7382", "#505797")) +
  geom_treemap_subgroup2_border(colour = "white", size = 3) +
  geom_treemap_subgroup_border(colour = "black", size = 5) +
  geom_treemap_subgroup_text(place = "centre", grow = T, alpha = 0.5, colour =
                             "black", fontface = "italic", min.size = 0) +
  geom_treemap_subgroup2_text(place = "centre", grow = T, alpha = 0.5, colour =
                             "white", fontface = "italic", min.size = 0) # +
  # geom_treemap_text(colour = "grey", place = "topleft", reflow = T)

```
:::

Detailed look at my publications by year and type: @cr-pub-bar

:::{#cr-pub-bar}
```{r}
library(paletteer) # for color palette

# Change Type to factor for better plotting
Products_ord <- Products |>
  mutate(Type = factor(Type, 
                       levels = c("Journal Article", "Presentation", "Agency Publication",
                                  "Poster", "Dashboard", "Template", "Website", 
                                  "Journal Issue", "Tutorial", "Book Chapter",
                                  "PICES Special Publication",
                                  "Content and Graphics")))

pub_interactive <- ggplot() +
  geom_bar_interactive(data = Products_ord, 
                       aes(x = Type, fill = Type,
                           tooltip = ifelse(!is.na(Link), Link, Title))) + 
  # geom_bar(data = Products_ord, aes(x = Type, fill = Type)) +
  scale_fill_paletteer_d("rcartocolor::Prism") +
  # scale_fill_paletteer_d("rcartocolor::Safe") + # looked a little chaotic
  facet_wrap(~Year) +
  labs(y = "Count") +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank())

girafe(ggobj = pub_interactive,
       options = list(
         opts_tooltip(
           opacity = 0.9
         )
       )
       )

```
:::

::::

::::{.cr-section}
## My Career Evolution

The focus of my work has changed over time _work in progress_: @cr-role-evolve


:::{#cr-role-evolve}
```{r}
library(ggbump)

# Create factor for role based on a combination of Type and Author
Products_role <- Products |>
  mutate(Role = NA)

for (r in seq(1, dim(Products_role)[1], 1)) {
  if (Products_role$Type[r] == "Template") {
    Products_role$Role[r] = "Instruction"
    } else if ((Products_role$Type[r] == "Dashboard" | 
                Products_role$Type[r] == "Website" |
                Products_role$Type[r] == "Content And Graphics")) {
      Products_role$Role[r] = "Data Visualization"
      } else {
        if(Products_role$Author[r] == "Supporting") {
          Products_role$Role[r] = "Data Analysis"
          } else {
            Products_role$Role[r] = "Project Leadership"
          }
      }
}
rm(r)

pub_roles <- Products_role |>
  count(Year, Role) |>
  mutate(ranking = rank(desc(n), ties.method = "first"), .by = Year)

# selected <- c("Presentation", "AgencyPublication", "JournalArticle", "Dashboard")

ggplot(pub_roles, aes(x = Year, y = n, group = Role)) +
  # geom_bump(linewidth = 0.5, color = "lightgrey", smooth = 7) +
  geom_bump(aes(color = Role), linewidth = 1, smooth = 7) # +
  # scale_y_reverse()

# Things to fix:
# - replace counts with rank (should be 1-4)
# - add in elements for which there's only a single year (Instruction)

```
:::

Add here: a sentence about what I'd like to do next and redirect to full cv/website/whatever

::::
Things to to/add (beyond what's noted in the comments in the code):  

* Add skills, professional development, etc. to resume section.  Perhaps using 
ggiraph so the scroller doesn't get too long.
* Figure out why the CV section heading isn't displaying properly, and why
subsequent figures don't display at all if the section header coding is added (`##`)  
  - Update: this problem is actually tied to a bug preventing headings that start
  with the letter _c_.  Weird.  <https://github.com/qmd-lab/closeread/discussions/186> 
  and <https://github.com/qmd-lab/closeread/issues/187>

* Figure out why:  
  - all interactive elements are available even before the plot calling them is 
  triggered,
  - there can only be interactive elements if no non-interactive plots follow them
  (this is why ggirafe wasn't/isn't working, as far as I can tell)  
    - Update: fixed this by adding a new closeread section for the non-interactive plots
  
* Figure out a figure to show the evolution of my career focus over time,
something like analysis (supporting author) to lead (first author) to data 
viz pivot (templates, tutorials, etc.)
* Some kind of ending, even if it's just, "to see more, head to...."  
* Replace all this with acknowledgements

