---
title: "Phoebe Woodworth-Jefcoats, PhD"
format: 
  closeread-html:
    cr-style:
      section-background-color: white
    theme: [zephyr, custom.scss]
---

Kaneohe, HI  |  (808) 358-7767  |  <phoebe.jefcoats@gmail.com>  
[pwj-dataviz.com](https://www.pwj-dataviz.com)  |  LinkedIn: [pwoodworth-jefcoats](http://www.linkedin.com/in/pwoodworth-jefcoats)  |  GitHub: [pwoodworth-jefcoats](https://github.com/pwoodworth-jefcoats)  |  ORCiD: [0000-0001-9353-923X](https://orcid.org/0000-0001-9353-923X)  

## Professional Summary
I have over 20 years of experience turning large datasets into easy-to-understand
graphics and reports, all backed by thorough data analysis.  I'm adept at workflows
that merge data analysis and communication product development, including incorporating
branding standards.  Across my work, I focus on using data to provide clarity, tell
stories, and inform decisions for audiences ranging from technical experts to casual
readers.  I embrace collaborative open science and contribute to the development of
tools, templates, best practice guides, and hands-on training.

::::{.cr-section}

## Resume

Here's a brief look at the jobs I've had and the degrees I've earned.

Employment @cr-jobs

:::{#cr-jobs}
```{r, message = FALSE}
# Load packages
library(tidyverse, quietly = TRUE)
library(here)

# Following an example from:
# https://r-graph-gallery.com/web-vertical-line-chart-with-ggplot2.html
# with an assist from phind.com and 
# https://github.com/clementrx/Closeread-Prize/blob/main/index.qmd

# Load data
jobs <- read.csv(here("CV", "Data", "Employment.csv"))
labels <- read.csv(here("CV", "Data", "TimelineLabels.csv"))
labels_jobs <- labels |>
  filter(category == "job")

# This is tedius, but not sure of a better way
lj1 <- labels |>
  filter(category == "job_1")
lj2 <- labels |>
  filter(category == "job_2")
lj3 <- labels |>
  filter(category == "job_3")

ggplot() +
  geom_segment(data = jobs, aes(x = Start, y = 10,
                                xend = End, yend = 10,
                                color = Employer),
               linewidth = 3,
               show.legend = FALSE) +
  geom_text(data = labels_jobs, aes(x = x, y = y, label = label),
            size = 4,
            hjust = 0,
            show.legend = FALSE) +
  geom_text(data = lj1, aes(x = x, y = y, label = label),
            color = "#003087",
            size = 4,
            hjust = 0,
            show.legend = FALSE) +
  geom_text(data = lj2, aes(x = x, y = y, label = label),
            color = "#77BDE7",
            size = 4,
            hjust = 0,
            show.legend = FALSE) +
  geom_text(data = lj3, aes(x = x, y = y, label = label),
            color = "#3366cc",
            size = 4,
            hjust = 0,
            show.legend = FALSE) +
  scale_y_continuous(
    limits = c(0, 100),
    position = "left") +
  scale_x_continuous(
    limits = c(2002, 2026)) +
  scale_color_manual(values = c("#77BDE7", "#3366cc", "#003087")) +
  theme_void() +
  coord_flip()

```
:::

Education @cr-schools

:::{#cr-schools}
```{r}
library(ggiraph) # For interactive elements

# Load data
school <- read.csv(here("CV", "Data", "Education.csv"))

labels_school <- labels |>
  filter(category == "degree")

# Build on previous plot
# which means replicating code from above
ggplot() +
  geom_segment(data = jobs, aes(x = Start, y = 10,
                                xend = End, yend = 10,
                                color = Employer),
               linewidth = 3,
               show.legend = FALSE) +
  geom_text(data = labels_jobs, aes(x = x, y = y, label = label),
            size = 4,
            hjust = 0,
            show.legend = FALSE) +
  geom_text(data = lj1, aes(x = x, y = y, label = label),
            color = "#003087",
            size = 4,
            hjust = 0,
            show.legend = FALSE) +
  geom_text(data = lj2, aes(x = x, y = y, label = label),
            color = "#77BDE7",
            size = 4,
            hjust = 0,
            show.legend = FALSE) +
  geom_text(data = lj3, aes(x = x, y = y, label = label),
            color = "#3366cc",
            size = 4,
            hjust = 0,
            show.legend = FALSE) +
  scale_y_continuous(
    limits = c(0, 100),
    position = "left") +
  scale_x_continuous(
    limits = c(2002, 2026)) +
  scale_color_manual(values = c("#77BDE7", "#3366cc", "#003087")) +
  theme_void() +
  coord_flip() +
# new stuff added to plot
  geom_point(data = school, aes(x = Date, y = 10),
             shape = 21, color = "white", fill = "black", size = 5, stroke = 0.7,
             show.legend = FALSE) +
  geom_text(data = labels_school, aes(x = x, y = y, label = label),
            size = 4,
            hjust = 0,
            show.legend = FALSE)
```
:::

Education (testing ggiraph for interactivity) @cr-inter-schools

:::{#cr-inter-schools}
```{r}
library(ggiraph) # For interactive elements

# Load data
school <- read.csv(here("CV", "Data", "Education.csv"))

labels_school <- labels |>
  filter(category == "degree")

# Build on previous plot
# which means replicating code from above
edu_interactive <- ggplot() +
  geom_segment(data = jobs, aes(x = Start, y = 10,
                                xend = End, yend = 10,
                                color = Employer),
               linewidth = 3,
               show.legend = FALSE) +
  geom_text(data = labels_jobs, aes(x = x, y = y, label = label),
            size = 4,
            hjust = 0,
            show.legend = FALSE) +
  geom_text(data = lj1, aes(x = x, y = y, label = label),
            color = "#003087",
            size = 4,
            hjust = 0,
            show.legend = FALSE) +
  geom_text(data = lj2, aes(x = x, y = y, label = label),
            color = "#77BDE7",
            size = 4,
            hjust = 0,
            show.legend = FALSE) +
  geom_text(data = lj3, aes(x = x, y = y, label = label),
            color = "#3366cc",
            size = 4,
            hjust = 0,
            show.legend = FALSE) +
  scale_y_continuous(
    limits = c(0, 100),
    position = "left") +
  scale_x_continuous(
    limits = c(2002, 2026)) +
  scale_color_manual(values = c("#77BDE7", "#3366cc", "#003087")) +
  theme_void() +
  coord_flip() +
# new stuff added to plot
  geom_point_interactive(data = school, aes(x = Date, y = 10, tooltip = Focus),
             shape = 21, color = "white", fill = "black", size = 5, stroke = 0.7,
             show.legend = FALSE) +
  geom_text(data = labels_school, aes(x = x, y = y, label = label),
            size = 4,
            hjust = 0,
            show.legend = FALSE)

girafe(ggobj = edu_interactive)

```
:::

## Placeholder head

Digging deeper, there's more to visualize. @cr-mt

:::{#cr-mt}
```{r}
ggplot() +
  geom_blank() +
  theme_void()
```
:::

For example, publications by year, type, and personal contribution: @cr-pub-tree

:::{#cr-pub-tree}
```{r}
# Decided to keep this for now
library(treemapify)

Products <- read_csv(here("CV", "Data", "Products.csv"), show_col_types = FALSE)

Products_byYearTypeAuthor <- Products %>%
  count(Year, Type, Author)

ggplot(Products_byYearTypeAuthor, aes(area = n, fill = Author, label = Author,
                                      subgroup = Year,
                                      subgroup2 = Type)) +
  geom_treemap() +
  scale_fill_discrete(name = "Authorship") +
  geom_treemap_subgroup2_border(colour = "white", size = 3) +
  geom_treemap_subgroup_border(colour = "black", size = 5) +
  geom_treemap_subgroup_text(place = "centre", grow = T, alpha = 0.5, colour =
                             "black", fontface = "italic", min.size = 0) +
  geom_treemap_subgroup2_text(place = "centre", grow = T, alpha = 0.5, colour =
                             "white", fontface = "italic", min.size = 0) # +
  # geom_treemap_text(colour = "grey", place = "topleft", reflow = T)

```
:::

We can dive even deeper to see what each of those products are.  Mouse
over the figure for details (eventually). @cr-pub-dot

:::{#cr-pub-dot}
```{r}
# Order publication types so that those with the greatest numbers are first.
Products_ord <- Products |>
  mutate(Type = factor(Type, 
                       levels = c("JournalArticle", "Presentation", "AgencyPublication",
                                  "Poster", "Dashboard", "Template", "Website", 
                                  "JournalIssue", "Tutorial", "ContentAndGraphics")))

# Split pubs apart by author role, then put them in order, then number them.
pubs_supp <- Products_ord |>
  filter(Author == "Supporting") |>
  arrange(Type) |>
  mutate(n = NA)

pubs_first <- Products_ord |>
  filter(Author == "First") |>
  arrange(Type) |>
  mutate(n = NA)

pubs_inv <- Products_ord |>
  filter(Author == "Invited") |>
  arrange(Type) |>
  mutate(n = NA)

pubs_ed <- Products_ord |>
  filter(Author == "Editor") |>
  arrange(Type) |>
  mutate(n = NA)

# Numbering within each year, for nice plotting
for (yr in seq(min(Products$Year), max(Products$Year), 1)) {
  supp_idx <- which(pubs_supp$Year == yr)
  first_idx <- which(pubs_first$Year == yr)
  inv_idx <- which(pubs_inv$Year == yr)
  ed_idx <- which(pubs_ed$Year == yr)
  
  if (length(supp_idx) > 0) {
    pubs_supp$n[supp_idx] = seq(1, length(supp_idx), 1)
  }
  
  if (length(first_idx) > 0) {
    pubs_first$n[first_idx] = seq(1, length(first_idx), 1)
  }
  
  if (length(inv_idx) > 0) {
    pubs_inv$n[inv_idx] = seq(1, length(inv_idx), 1)
  }
  
  if (length(ed_idx) > 0) {
    pubs_ed$n[ed_idx] = seq(1, length(ed_idx), 1)
  }
}

# Plot everthing
ggplot() +
  geom_point(data = pubs_first, aes(x = Year - 0.15, y = n, color = Type)) +
  geom_point(data = pubs_supp, aes(x = Year - 0.05, y = n, color = Type)) +
  geom_point(data = pubs_inv, aes(x = Year + 0.05, y = n, color = Type)) +
  geom_point(data = pubs_ed, aes(x = Year + 0.15, y = n, color = Type))

```
:::

Another possible way to do this (work in progress) @cr-pub-bar

:::{#cr-pub-bar}
```{r}
pubs_first$Year = pubs_first$Year - 0.3
pubs_supp$Year = pubs_supp$Year - 0.1
pubs_inv$Year = pubs_inv$Year + 0.1
pubs_ed$Year = pubs_ed$Year + 0.3

ggplot() +
  geom_bar(data = pubs_first, aes(x = Year, fill = Type), width = 0.2) +
  geom_bar(data = pubs_supp, aes(x = Year, fill = Type), width = 0.2) +
  geom_bar(data = pubs_inv, aes(x = Year, fill = Type), width = 0.2) +
  geom_bar(data = pubs_ed, aes(x = Year, fill = Type), width = 0.2)
```
:::

(work in progress)
We could also look at how the types of publications evolve over time @cr-pub-evolve

:::{#cr-pub-evolve}
```{r}
library(ggbump)

pub_types <- Products_ord |>
  count(Year, Type) |>
  filter(Year > 2019) |>
  mutate(ranking = rank(desc(n), ties.method = "first"), .by = Year)

selected <- c("Presentation", "AgencyPublication", "JournalArticle")

ggplot(pub_types, aes(x = Year, y = ranking, group = Type)) +
  geom_bump(linewidth = 0.5, color = "lightgrey", smooth = 7,
            data = ~. |> filter(Type %in% selected)) +
  geom_bump(aes(color = Type), linewidth = 1, smooth = 7, 
            data = ~. |> filter(Type %in% selected)) +
  scale_y_reverse()

```
:::

::::
Things to to/add (beyond what's noted in the comments in the code):  

* Add skills, professional development, etc. to resume section.  Perhaps using 
ggiraph so the scroller doesn't get too long.
* Figure out why the CV section heading isn't displaying properly, and why
subsequent figures don't display at all if the section header coding is added (`##`)  
  - Update: this problem is actually tied to a bug preventing headings that start
  with the letter _c_.  Weird.  <https://github.com/qmd-lab/closeread/discussions/186> 
  and <https://github.com/qmd-lab/closeread/issues/187>

* Make the treemap look nice (nice colors, legible text)  
  - Will do this once figure is complete so I can be sure the colors will work in 
  the final plot.  
* Add additional years to treemap fig  
* Add grouped/stacked bar alternative (both as an alternative to the treemap and
as an alternative to traditional stacked or grouped bar charts)  
* Figure out a figure to show the evolution of my career focus over time,
something like analysis (supporting author) to lead (first author) to data 
viz pivot (templates, tutorials, etc. [and add the rest of these to Products.csv])
* Maybe something to show where I've published (maybe vs. where I've reviewed for?) 
and to highlight accomplishments like publishing in *Nature*

