---
title: "Phoebe Woodworth-Jefcoats, PhD"
format: 
  closeread-html:
    cr-style:
      section-background-color: white
    theme: [zephyr, custom.scss]
---

Kaneohe, HI  |  (808) 358-7767  |  <phoebe.jefcoats@gmail.com>  
[pwj-dataviz.com](https://www.pwj-dataviz.com)  |  LinkedIn: [pwoodworth-jefcoats](http://www.linkedin.com/in/pwoodworth-jefcoats)  |  GitHub: [pwoodworth-jefcoats](https://github.com/pwoodworth-jefcoats)  |  ORCiD: [0000-0001-9353-923X](https://orcid.org/0000-0001-9353-923X)  

## Professional Summary
I have over 20 years of experience turning large datasets into easy-to-understand
graphics and reports, all backed by thorough data analysis.  I'm adept at workflows
that merge data analysis and communication product development, including incorporating
branding standards.  Across my work, I focus on using data to provide clarity, tell
stories, and inform decisions for audiences ranging from technical experts to casual
readers.  I embrace collaborative open science and contribute to the development of
tools, templates, best practice guides, and hands-on training.

::::{.cr-section}

## Resume

Here's a brief look at the jobs I've had and the degrees I've earned.

Employment @cr-jobs

:::{#cr-jobs}
```{r, message = FALSE}
# Load packages
library(tidyverse, quietly = TRUE)
library(here)

# Following an example from:
# https://r-graph-gallery.com/web-vertical-line-chart-with-ggplot2.html
# with an assist from phind.com and 
# https://github.com/clementrx/Closeread-Prize/blob/main/index.qmd

# Load data
jobs <- read.csv(here("CV", "Data", "Employment.csv"))
labels <- read.csv(here("CV", "Data", "TimelineLabels.csv"))
labels_jobs <- labels |>
  filter(category == "job")

# This is tedius, but not sure of a better way
lj1 <- labels |>
  filter(category == "job_1")
lj2 <- labels |>
  filter(category == "job_2")
lj3 <- labels |>
  filter(category == "job_3")

ggplot() +
  geom_segment(data = jobs, aes(x = Start, y = 10,
                                xend = End, yend = 10,
                                color = Employer),
               linewidth = 3,
               show.legend = FALSE) +
  geom_text(data = labels_jobs, aes(x = x, y = y, label = label),
            size = 4,
            hjust = 0,
            show.legend = FALSE) +
  geom_text(data = lj1, aes(x = x, y = y, label = label),
            color = "#003087",
            size = 4,
            hjust = 0,
            show.legend = FALSE) +
  geom_text(data = lj2, aes(x = x, y = y, label = label),
            color = "#77BDE7",
            size = 4,
            hjust = 0,
            show.legend = FALSE) +
  geom_text(data = lj3, aes(x = x, y = y, label = label),
            color = "#3366cc",
            size = 4,
            hjust = 0,
            show.legend = FALSE) +
  scale_y_continuous(
    limits = c(0, 100),
    position = "left") +
  scale_x_continuous(
    limits = c(2002, 2026)) +
  scale_color_manual(values = c("#77BDE7", "#3366cc", "#003087")) +
  theme_void() +
  coord_flip()

```
:::

Education @cr-schools

:::{#cr-schools}
```{r}
# Load data
school <- read.csv(here("CV", "Data", "Education.csv"))

labels_school <- labels |>
  filter(category == "degree")

# Build on previous plot
# which means replicating code from above
ggplot() +
  geom_segment(data = jobs, aes(x = Start, y = 10,
                                xend = End, yend = 10,
                                color = Employer),
               linewidth = 3,
               show.legend = FALSE) +
  geom_text(data = labels_jobs, aes(x = x, y = y, label = label),
            size = 4,
            hjust = 0,
            show.legend = FALSE) +
  geom_text(data = lj1, aes(x = x, y = y, label = label),
            color = "#003087",
            size = 4,
            hjust = 0,
            show.legend = FALSE) +
  geom_text(data = lj2, aes(x = x, y = y, label = label),
            color = "#77BDE7",
            size = 4,
            hjust = 0,
            show.legend = FALSE) +
  geom_text(data = lj3, aes(x = x, y = y, label = label),
            color = "#3366cc",
            size = 4,
            hjust = 0,
            show.legend = FALSE) +
  scale_y_continuous(
    limits = c(0, 100),
    position = "left") +
  scale_x_continuous(
    limits = c(2002, 2026)) +
  scale_color_manual(values = c("#77BDE7", "#3366cc", "#003087")) +
  theme_void() +
  coord_flip() +
# new stuff added to plot
  geom_point(data = school, aes(x = Date, y = 10),
             shape = 21, color = "white", fill = "black", size = 5, stroke = 0.7,
             show.legend = FALSE) +
  geom_text(data = labels_school, aes(x = x, y = y, label = label),
            size = 4,
            hjust = 0,
            show.legend = FALSE)

```
:::

## Test head

Digging deeper, there's more to visualize. @cr-mt

:::{#cr-mt}
```{r}
ggplot() +
  geom_blank() +
  theme_void()
```
:::

For example, publications by year, type, and personal contribution: @cr-pub-tree

:::{#cr-pub-tree}
```{r}
# Decided to keep this for now
library(treemapify)

Products <- read_csv(here("CV", "Data", "Products.csv"), show_col_types = FALSE)

Products_byYearTypeAuthor <- Products %>%
  count(Year, Type, Author)

ggplot(Products_byYearTypeAuthor, aes(area = n, fill = Author, label = Author,
                                      subgroup = Year,
                                      subgroup2 = Type)) +
  geom_treemap() +
  scale_fill_discrete(name = "Authorship") +
  geom_treemap_subgroup2_border(colour = "white", size = 3) +
  geom_treemap_subgroup_border(colour = "black", size = 5) +
  geom_treemap_subgroup_text(place = "centre", grow = T, alpha = 0.5, colour =
                             "black", fontface = "italic", min.size = 0) +
  geom_treemap_subgroup2_text(place = "centre", grow = T, alpha = 0.5, colour =
                             "white", fontface = "italic", min.size = 0) # +
  # geom_treemap_text(colour = "grey", place = "topleft", reflow = T)

```
:::

We can dive even deeper to see what each of those products are.  Mouse
over the figure for details.

::::
Things to to/add (beyond what's noted in the comments in the code):  

* Add skills, professional development, etc. to resume
* Figure out why the CV section heading isn't displaying properly, and why
subsequent figures don't display at all if the section header coding is added (`##`)  
  - Update: this problem appears to be a documented bug.  No fix yet.  For more, see:  
  <https://github.com/quarto-dev/quarto-cli/issues/12470>  
and  
<https://github.com/qmd-lab/closeread/issues/176>  
  - Subsequent update: this problem actually seems to be tied to headings that start
  with the letter _c_.  Weird.  <https://github.com/qmd-lab/closeread/discussions/186>

* Make the treemap look nice (nice colors, legible text)  
  - Will do this once figure is complete so I can be sure the colors will work in 
  the final plot.  
* Add additional years to treemap fig  
* Add grouped/stacked bar alternative (both as an alternative to the treemap and
as an alternative to traditional stacked or grouped bar charts)  
* Figure out a figure to show the evolution of my career focus over time,
something like analysis (supporting author) to lead (first author) to data 
viz pivot (templates, tutorials, etc. [and add the rest of these to Products.csv])
* Maybe something to show where I've published (maybe vs. where I've reviewed for?) 
and to highlight accomplishments like publishing in *Nature*

