---
title: "Phoebe Woodworth-Jefcoats, PhD"
format:
  closeread-html:
    cr-style:
      section-background-color: white
    theme: [zephyr, custom.scss]
---

Kaneohe, HI  |  (808) 358-7767  |  <phoebe.jefcoats@gmail.com>  
[pwj-dataviz.com](https://www.pwj-dataviz.com)  |  LinkedIn: [pwoodworth-jefcoats](http://www.linkedin.com/in/pwoodworth-jefcoats)  |  GitHub: [pwoodworth-jefcoats](https://github.com/pwoodworth-jefcoats)  |  ORCiD: [0000-0001-9353-923X](https://orcid.org/0000-0001-9353-923X)  

## Professional Summary
I have over 20 years of experience turning large datasets into easy-to-understand
graphics and reports, all backed by thorough data analysis.  I'm adept at workflows
that merge data analysis and communication product development, including incorporating
branding standards.  Across my work, I focus on using data to provide clarity, tell
stories, and inform decisions for audiences ranging from technical experts to casual
readers.  I embrace collaborative open science and contribute to the development of
tools, templates, best practice guides, and hands-on training.

```{r}
#| include: false
#| message: false
#| warning: false

# Global setup
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE
)
```

::::{.cr-section}

## Resume

Here's a brief look at the jobs I've had and the degrees I've earned.

Employment @cr-jobs

:::{#cr-jobs}
```{r, message = FALSE}
# Load packages
library(tidyverse, quietly = TRUE)
library(here)
library(ggiraph) # For interactive elements

# Following an example from:
# https://r-graph-gallery.com/web-vertical-line-chart-with-ggplot2.html
# with an assist from phind.com and 
# https://github.com/clementrx/Closeread-Prize/blob/main/index.qmd

# Load data
jobs <- read.csv(here("CV", "Data", "Employment.csv"))
labels <- read.csv(here("CV", "Data", "TimelineLabels.csv"))
labels_jobs <- labels |>
  filter(category == "job")

# This is tedius, but not sure of a better way
lj1 <- labels |>
  filter(category == "job_1")
lj2 <- labels |>
  filter(category == "job_2")
lj3 <- labels |>
  filter(category == "job_3")

employ_interactive <- ggplot() +
  geom_segment_interactive(data = jobs, aes(x = Start, y = 10,
                                            xend = End, yend = 10,
                                            color = Employer,
                                            tooltip = Focus),
                           linewidth = 3,
                           show.legend = FALSE) +
  geom_text(data = labels_jobs, aes(x = x, y = y, label = label),
            size = 4,
            hjust = 0,
            show.legend = FALSE) +
  geom_text(data = lj1, aes(x = x, y = y, label = label),
            color = "#003087",
            size = 4,
            hjust = 0,
            show.legend = FALSE) +
  geom_text(data = lj2, aes(x = x, y = y, label = label),
            color = "#77BDE7",
            size = 4,
            hjust = 0,
            show.legend = FALSE) +
  geom_text(data = lj3, aes(x = x, y = y, label = label),
            color = "#3366cc",
            size = 4,
            hjust = 0,
            show.legend = FALSE) +
  scale_y_continuous(
    limits = c(0, 100),
    position = "left") +
  scale_x_continuous(
    limits = c(2002, 2026)) +
  scale_color_manual(values = c("#77BDE7", "#3366cc", "#003087")) +
  theme_void() +
  coord_flip() 

girafe(ggobj = employ_interactive,
       options = list(
         opts_tooltip(
           opacity = 0.9
         )
       )
       )

```
:::

Education @cr-schools

:::{#cr-schools}
```{r}
# Load data
school <- read.csv(here("CV", "Data", "Education.csv"))

labels_school <- labels |> 
  filter(category == "degree")

# Build on previous plot
# which means replicating code from above
edu_interactive <- ggplot() +
geom_segment_interactive(data = jobs, aes(x = Start, y = 10,
                                            xend = End, yend = 10,
                                            color = Employer,
                                            tooltip = Focus),
                           linewidth = 3,
                           show.legend = FALSE) +
geom_text(data = labels_jobs, aes(x = x, y = y, label = label),
          size = 4,
          hjust = 0,
          show.legend = FALSE) +
geom_text(data = lj1, aes(x = x, y = y, label = label),
          color = "#003087",
          size = 4,
          hjust = 0,
          show.legend = FALSE) +
geom_text(data = lj2, aes(x = x, y = y, label = label),
          color = "#77BDE7",
          size = 4,
          hjust = 0,
          show.legend = FALSE) +
geom_text(data = lj3, aes(x = x, y = y, label = label),
          color = "#3366cc",
          size = 4,
          hjust = 0,
          show.legend = FALSE) +
scale_y_continuous(
  limits = c(0, 100),
  position = "left") +
scale_x_continuous(
  limits = c(2002, 2026)) +
scale_color_manual(values = c("#77BDE7", "#3366cc", "#003087")) +
theme_void() +
coord_flip() +
# new stuff added to plot
geom_point_interactive(data = school, aes(x = Date, y = 10, tooltip = Focus),
           shape = 21, color = "white", fill = "black", size = 5, stroke = 0.7,
           show.legend = FALSE) +
geom_text(data = labels_school, aes(x = x, y = y, label = label),
          size = 4,
          hjust = 0,
          show.legend = FALSE)

girafe(ggobj = edu_interactive,
       options = list(
         opts_tooltip(
           opacity = 0.9
         )
       )
       )
```
:::

## Placeholder head

Digging deeper, there's more to visualize. @cr-mt

:::{#cr-mt}
```{r}
ggplot() +
  geom_blank() +
  theme_void()
```
:::

::::
